%-------------------------
% TEMPLATE INFO
% CV for Northeastern University Faculty in Latex
% Author : Zoe Kearney
% Based off of: https://www.overleaf.com/latex/templates/coles-resume-template/qhpynjcvjpcj
% Follows: https://theprofessorisin.com/2016/08/19/dr-karens-rules-of-the-academic-cv/
% License : MIT

% Used and modified by: Lionel Chambon
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=1in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{tabularx} % For header
\usepackage{fontawesome}
\usepackage{enumitem} % For bullet points
\usepackage{ragged2e}

\usepackage[
    pdftex,            % Enable PDF features
    colorlinks=true,    % Use colored text instead of boxes
    linkcolor=blue,     % Color for internal links
    urlcolor=blue,      % Color for email and external links
    citecolor = deepblue,
    pdfborder={0 0 0},  % No border around links
    plainpages=false
]{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large LIONEL CHAMBON}\\[3pt] % Name
\textbf{Graduate Student in Economics}\\[1pt] % One-liner
Paris, France \ $|$ \  +33 624 894 241   % Contact info

\begin{tabularx}{\linewidth}{X}
\centering
\href{https://github.com/lionelchambon}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/lionel-chambon-500b64187/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://lionelchambon.github.io}{\raisebox{-0.05\height}\faGlobe\ Website} \ $|$ \ 
\href{mailto:lionel.chambon@sciencespo.fr}{\raisebox{-0.05\height}\faEnvelope\ E-Mail} \ 
\end{tabularx}

\end{center}

%------------------------

% Education Section
\section*{EDUCATION}

\noindent
\newline
\begin{minipage}[t]{0.7\textwidth}
  \textbf{M.Res. in Economics}
\end{minipage}%
\begin{minipage}[t]{0.3\textwidth}
  \raggedleft \textbf{2023 -- 2025}
\end{minipage}
\\
\textit{Sciences Po School of Research (PhD-Track)} \\
GPA after first year of courses: 3.8
\begin{itemize}[noitemsep, topsep=0pt, left=0.65cm]
    \item Graduate courses in econometrics, micro- and macroeconomics. Instruction in Stata, R, Julia. 
    \item Sample \href{https://lionelchambon.github.io/coursework/}{coursework} and \href{https://github.com/lionelchambon}{coding samples} are available on my website. \\
\end{itemize} 

\noindent
\begin{minipage}[t]{0.7\textwidth}
  \textbf{B.A. in Political Science and Economics}
\end{minipage}%
\begin{minipage}[t]{0.3\textwidth}
  \raggedleft \textbf{2020 -- 2023}
\end{minipage}
\\
\textit{Sciences Po Undergraduate College} \\
\textit{Cum laude} distinction. GPA: 4.0
\begin{itemize}[noitemsep, topsep=0pt, left=0.65cm]
    \item Major in Economics. Minor in Middle Eastern studies included courses in Arabic and politics focused on the MENA region. 
    \item Academic exchange year at the University of St. Andrews, Scotland (2022-2023), placed on Dean's List. 
\end{itemize} 

%------------------------

% Employment Section
\section*{PROFESSIONAL EXPERIENCE}

\noindent
\newline
\begin{minipage}[t]{0.7\textwidth}
  \textbf{Deutsche Bundesbank}
\end{minipage}%
\begin{minipage}[t]{0.3\textwidth}
  \raggedleft \textbf{Jun -- Aug 2024}
\end{minipage}
\\
\textit{Frankfurt-am-Main, Germany} \\ 
Summer intern, General Directorate Economics 
\begin{itemize}[noitemsep, topsep=0pt, left=0.65cm]
    \item  Tasked with an empirical project to investigate private consumption dynamics in the Euro area. I estimate an error-correction model to compare consumption trends before and after the COVID-19 pandemic and find stronger effects of income and financial wealth variables since 2020.
    \item A detailed project report is available \href{https://lionelchambon.github.io/files/Chambon_BundesbankProject_EN.pdf}{here.}
    \\
\end{itemize}

\noindent
\begin{minipage}[t]{0.7\textwidth}
  \textbf{German--Tunisian Chamber of Commerce (AHK Tunesien)}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \raggedleft \textbf{Jun -- Aug 2023}
\end{minipage}
\\
\textit{Tunis, Tunisia} \\ 
Summer intern, DEinternational services department 
\begin{itemize}[noitemsep, topsep=0pt, left=0.65cm]
    \item Tasked with researching and editing two market analysis reports for the German Ministry of Economics Affairs and Climate Action. Frequently translated between German, French, and English. 
\end{itemize} 

%------------------------

% Quantitative Skills Section 
\section*{QUANTITATIVE SKILLS}

\noindent
\textbf{Programming:} R, Julia, EViews, Stata \\
\textbf{Data experience:} Macroeconomic time-series from Eurostat and European Commission \\
\textbf{Time-series econometrics:} Error-correction models, factor models, local projections \\
\textbf{Mico-econometrics}: Linear regression, instrumental variables, Monte-Carlo simulations

%------------------------

% Other Skills Section 
\section*{OTHER SKILLS \& PERSONAL INTERESTS}

\noindent
\textbf{Languages}: German, French (native), English (C2), Arabic (B2), Tunisian Arabic dialect (A2) \\
\noindent
\textbf{Software:}  Microsoft Office, \LaTeX \\
\textbf{Personal Interests:} Historical and crime novels, running, German literature

%------------------------

% References Section 

\section*{REFERENCES}

\noindent
\begin{minipage}[t]{0.32\textwidth} 
    \textbf{Dr. Johannes Hoffmann} \\
    \textit{Department Chair} \\
    International and Euro Area Economy Division \\
    Deutsche Bundesbank \\
    \href{mailto:johannes.hoffmann@bundesbank.de}{johannes.hoffmann@bundesbank.de} 
\end{minipage}

\vspace{1cm}
\begin{FlushRight}
        \textit{Last updated: January 2025}
\end{FlushRight}



% End document
\end{document}
